Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-08-26 paper/supplemental_information.Rmd
various revisons

---
title: "Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
---

@@

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution for each dataset, using three-month bins.", fig.pos="h!"}

@@

```{r longitudinal_descriptives, fig.cap="\\label{fig:longitudinal_descriptives} Number of administrations for datasets with repeated measurements, plotted by dataset.", fig.pos="h!"}

d_sub_long <- d_sub |>
  filter(subject_id %in% longitudinal$subject_id) |>
  group_by(subject_id) |>
  arrange(age) |>
  mutate(admin_num = 1:n(), 
         delta_t = age - age[1])

ggplot(d_sub_long, 
       aes(x = delta_t, fill = dataset_name)) +
  geom_histogram(binwidth = 1) + 
  scale_fill_solarized(name = "Dataset") +
  theme(legend.position = "bottom") + 
  # facet_wrap(~dataset_name) + 
  xlab("Age since first test") + 
  ylab("Number of participants")
```

@@

Table \ref{tab:accmods} shows model comparison measures between for different models of the functional form of the relationship between accuracy and age and Table \ref{tab:rtmods} shows the same for reaction time. Age gradients are estimated substantially better with long window accuracies. Note that there are a greater number of observations for short window accuracies due to less missing data. We speculate that, on average, more participants looked away from the screen towards the end of trials, leading to a greater number of exclusions of long window trials based on the 50% criterion. Note that the total percentage of trials excluded is still small for both measures: `r round(mean(is.na(d_trial$long_window_accuracy)), 2)`% for long window accuracy and `r round(mean(is.na(d_trial$short_window_accuracy)), 2)`% for short window accuracy.

@@

Note that with our current dataset we cannot specifically determine whether within-individual patterns of change conform to linear, power law, or exponential developmental patterns (Heathcote, Brown, \& Mewhort, 2000). Our current results apply to the form of the age gradient as opposed to the form of any individual's pattern of developmental change.

@@

@@

@@

# References

>>>>

---
title: "Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
  - \renewcommand{\thefigure}{S\arabic{figure}}
  - \renewcommand{\thetable}{S\arabic{table}}

---

@@

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution of unique participants for each dataset, using three-month bins.", fig.pos="h!"}

@@

```{r longitudinal_descriptives, fig.cap="\\label{fig:longitudinal_descriptives} Distribution of retest administrations across datasets with repeated measurements, colored by dataset. Each count indicates a retest administration (initial administrations are excluded). Administrations listed with a retest interval of 0 indicate retests within a month of the initial administration.", fig.pos="h!"}

d_sub_long <- d_sub |>
  filter(subject_id %in% longitudinal$subject_id) |>
  group_by(subject_id) |>
  arrange(age) |>
  mutate(delta_t = age - age[1])

ggplot(filter(d_sub_long, admin_num > 1), 
       aes(x = delta_t, fill = dataset_name)) +
  geom_histogram(binwidth = 1) + 
  scale_fill_solarized(name = "Dataset") +
  theme(legend.position = "bottom") + 
  # facet_wrap(~dataset_name) + 
  xlab("Months since first test administration") + 
  ylab("Number of administrations")
```

# Reaction Time Computation

Eye-tracking data are stored in Peekbank as a time series of fixations to specific areas of interest (in particular, the target and distractor on each trial). Other fixations can be to areas not in the target or distractor as well to off-screen areas. This time series has a uniform sample rate of 25ms/sample, based on resampling of the data in Peekbank to 40 Hz during preprocessing [@zettersten2023peekbank]. Reaction times are computed by filtering trials to only those on which the child is fixating the distractor at the point of disambiguation ($t=0$) and then finding those trials on which the first non-missing fixation is to the target (hence excluding trials without a shift and trials on which a shift is to an off-screen location). The reaction time is then the total time from $t=0$ to the first timestep during which the child fixates the target. Consistent with standard practice in the literature following Fernald et al. (2008), RTs that are shorter than 367 ms are excluded as they are too short to be considered a response to the stimulus.

# Separability of Variability from Other Measures

## Reaction Time

```{r}
library(fitdistrplus)
library(statmod)

library(gamlss.dist)

rt_fitting  <- d_sub |>
  ungroup() |>
  filter(!is.na(rt)) |>
  mutate(age_bin = cut(age,
                       breaks = c(0,12,15,18,21,24,27,30,36,60), 
                       labels = c("<12", "12-15","15-18", "18-21", 
                                  "21-24", "24-27","27-30","30-36", ">36"))) |>
  select(age_bin, rt)

norm <- fitdist(rt_fitting$rt, distr = "norm", method = "mle")
lnorm <- fitdist(rt_fitting$rt, distr = "lnorm", method = "mle")
wald <- fitdist(rt_fitting$rt, distr = "invgauss", method = "mle", 
                start = list(mean = 1, shape = 1, dispersion = 1))
exgaus <- fitdist(rt_fitting$rt, distr = "exGAUS", method = "mle", 
                  start = list(mu = 1000, sigma = 500, nu = 1), 
                  lower = c(0, 0, 0))

BIC(norm)
BIC(lnorm)
BIC(wald)
BIC(exgaus)

rt_fits <- rt_fitting |>
  group_by(age_bin) |>
  nest(rt) |>
  mutate(
    norm = map(data, \(d) fitdist(d$rt, distr = "norm", method = "mle")),
    lnorm = map(data, \(d) fitdist(d$rt, distr = "lnorm", method = "mle")),
    wald = map(data, \(d) fitdist(d$rt, distr = "invgauss", method = "mle", 
                                  start = list(mean = 1, shape = 1, dispersion = 1))),
    exgaus = map(data, \(d) fitdist(d$rt, distr = "exGAUS", method = "mle", 
                                    start = list(mu = 1000, sigma = 500, nu = 1), 
                                    lower = c(0, 0, 0)))) |>
  select(-data) |>
  pivot_longer(norm:exgaus, names_to = "distribution", values_to = "fit") |>
  mutate(BIC = map_dbl(fit, BIC)) |>
  group_by(age_bin) |>
  mutate(min_bic = BIC == min(BIC))

ggplot(rt_fits, 
       aes(x = distribution, y = BIC, col = min_bic)) + 
  geom_point(stat = "identity", position = "dodge") + 
  scale_color_solarized(name = "Lowest BIC") + 
  xlab("Age bin") + 
  ylab("BIC") + 
  coord_flip() + 
  facet_wrap(~age_bin, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r}
rt_hist_data <- d_sub |>
  mutate(
    age_bin = cut(age,
                  breaks = c(0,12,15,18,21,24,27,30,36,60), 
                  labels = c("<12", "12-15","15-18", "18-21", 
                             "21-24", "24-27","27-30","30-36", ">36")))

bw = .2

rt_hist_summary <- rt_hist_data |>
  group_by(age_bin) |>
  summarise(m = mean(log_rt, na.rm = TRUE), 
            sd = sd(log_rt, na.rm = TRUE), 
            n = n()) |>
  expand_grid(log_rt = seq(6,8,.01)) |>
  mutate(norm = dnorm(log_rt, mean = m, sd = sd) * n * bw)

ggplot(rt_hist_data,
       aes(x = log_rt)) + 
  geom_histogram(binwidth = bw) + 
  geom_line(data = rt_hist_summary, aes(x = log_rt, y = norm), col = "blue") +
  xlab("Log RT (ms)") + 
  ylab("Number of trials") + 
  facet_wrap(~age_bin)+ 
  theme_few()
```

## Accuracy

```{r}
acc_hist_data <- d_sub |>
  mutate(
    age_bin = cut(age,
                  breaks = c(0,12,15,18,21,24,27,30,36,60), 
                  labels = c("<12", "12-15","15-18", "18-21", 
                             "21-24", "24-27","27-30","30-36", ">36")))

bw = .025

acc_hist_summary <- acc_hist_data |>
  group_by(age_bin) |>
  summarise(m = mean(long_window_accuracy, na.rm = TRUE),
            sd = sd(long_window_accuracy, na.rm = TRUE),
            n = n()) |>
  expand_grid(acc = seq(0,1,.01)) |>
  mutate(norm = dnorm(acc, mean = m, sd = sd) * n * bw)

ggplot(acc_hist_data,
       aes(x = long_window_accuracy)) + 
  geom_histogram(binwidth = bw) + 
  geom_line(data = acc_hist_summary, aes(x = acc, y = norm), col = "blue") +
  xlab("Long Window Accuracy") + 
  ylab("Number of trials") + 
  facet_wrap(~age_bin) + 
  theme_few()
```

```{r}

acc_fitting  <- d_sub |>
  ungroup() |>
  filter(!is.na(long_window_accuracy)) |>
  mutate(age_bin = cut(age,
                       breaks = c(0,12,15,18,21,24,27,30,36,60), 
                       labels = c("<12", "12-15","15-18", "18-21", 
                                  "21-24", "24-27","27-30","30-36", ">36"))) |>
  select(age_bin, long_window_accuracy)

norm <- fitdist(acc_fitting$long_window_accuracy, distr = "norm", method = "mle")
beta <- fitdist(acc_fitting$long_window_accuracy, distr = "beta", method = "mle")

BIC(norm)
BIC(beta)
```

```{r}

acc_fits <- acc_fitting |>
  group_by(age_bin) |>
  nest(long_window_accuracy) |>
  mutate(
    norm = map(data, \(d) fitdist(d$long_window_accuracy, distr = "norm", method = "mle")),
    beta = map(data, \(d) fitdist(d$long_window_accuracy, distr = "beta", method = "mle"))) |>
  select(-data) |>
  pivot_longer(norm:beta, names_to = "distribution", values_to = "fit") |>
  mutate(BIC = map_dbl(fit, BIC)) |>
  group_by(age_bin) |>
  mutate(min_bic = BIC == min(BIC))

ggplot(acc_fits, 
       aes(x = distribution, y = BIC, col = min_bic)) + 
  geom_point(stat = "identity", position = "dodge") + 
  scale_color_solarized(name = "Lowest BIC") + 
  xlab("Age bin") + 
  ylab("BIC") + 
  coord_flip() + 
  facet_wrap(~age_bin, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

Table \ref{tab:accmods} shows model comparison measures between for different models of the functional form of the relationship between accuracy and age and Table \ref{tab:rtmods} shows the same for reaction time. Age gradients are estimated substantially better with long window accuracies. Note that there are a greater number of observations for short window accuracies due to less missing data. We speculate that, on average, more participants looked away from the screen towards the end of trials, leading to a greater number of exclusions of long window trials based on the 50% criterion. Note that the total percentage of trials excluded is still small for both measures: `r round(mean(is.na(d_trial$long_window_accuracy)), 3)*100`% for long window accuracy and `r round(mean(is.na(d_trial$short_window_accuracy)), 3)*100`% for short window accuracy.

@@

@@

# Power Law Fits

In the literature on the "law of practice", although the log-log relationship we observed is commonly present in the aggregate across individuals, the situation is substantially more complex when relationships are measured within individuals. The best fitting curves for individuals are often exponentials or delayed exponentials  (Evans et al., 2018; Heathcote, Brown, \& Mewhort, 2000). With our current dataset we cannot specifically determine whether within-individual patterns of change conform to linear, power law, or exponential developmental patterns unfortunately, because we have insufficient data about individuals' improvement across time. Thus, our current results apply to the form of the age gradient as opposed to the form of any individual's pattern of developmental change.

Nevertheless, here we test for other forms of the aggregate relationship between age and reaction time. In particular, we consider further model comparison between the

```{r rt_mods}
rt_more_mods_lmer <- 
  list(log_log = lmer(log_rt ~ log_age_s + 
                        (log_age_s | dataset_name) + (1 | subject_id), 
                      data = d_trial),
       log_log_plus = lmer(log_rt ~ log_age_s + age_s +  
                             (log_age_s + age_s | dataset_name) + (1 | subject_id), 
                           data = d_trial), 
       lin_poly2 = lmer(rt ~ poly(age_s, 2) +  
                        (age_s | dataset_name) + (1 | subject_id), 
                      data = d_trial),
       lin_poly3 = lmer(rt ~ poly(age_s, 3) +  
                        (age_s | dataset_name) + (1 | subject_id), 
                      data = d_trial))

rt_more_mods_lmer_summary <- map_df(rt_more_mods_lmer, ~broom.mixed::glance(.x)) |>
  mutate(model = names(rt_more_mods_lmer), 
         r2 = map_dbl(rt_more_mods_lmer, ~performance::r2_nakagawa(.x)$R2_conditional))
```

# Mixed effects model specifications

Here we provide specifications for the mixed effects models used in the main text. These models are used to estimate the relationship between age and the primary variables of interest, controlling for dataset and subject-level variability.

\verbatim{lmer(long_window_acc_var ~ log_age_s + (log_age_s | dataset_name) + (1 | subject_id)}

FIXME

@@

# Factor Analysis: First Administrations

```{r}
d_sub_mat_firstadmin <- d_sub_firstadmin |>
  ungroup() |>
  select(dataset_name, log_rt, log_rt_var, long_window_accuracy, long_window_acc_var, prod, comp, age, log_age)

d_sub_mat_firstadmin_s <- d_sub_mat_firstadmin |>
  ungroup() |>
  mutate(across(all_of(c("log_rt", "log_rt_var", "long_window_accuracy", 
                         "long_window_acc_var", "prod", "comp")), 
                ~ age_scale(.x, age))) 
```

```{r}
fit3_firstadmin <- cfa(fa3_model, d_sub_mat_firstadmin_s, 
                       std.lv=TRUE, missing='fiml')

fit_stats_firstadmin <- suppressMessages(summary(fit3_firstadmin, 
                                                 fit.measures=TRUE, 
                                                 standardize=TRUE))
```

```{r}
d_sub_mat_firstadmin_s_renamed <- d_sub_mat_firstadmin_s |>
  rename(acc = long_window_accuracy, 
         acc_sd = long_window_acc_var, 
         log_rt_sd = log_rt_var)

fit3_age_firstadmin <- cfa(fa3_age_model, 
                           d_sub_mat_firstadmin_s_renamed, 
                           std.lv=TRUE, missing='fiml')

fit3_age_summary_firstadmin <- 
  suppressMessages(summary(fit3_age_firstadmin, 
                           fit.measures=TRUE, 
                           standardize=TRUE))
```

```{r}
library(semoutput)
semoutput::sem_fitmeasures(fit3)
semoutput::sem_fitmeasures(fit3_firstadmin)
semoutput::sem_fitmeasures(fit3_age)
semoutput::sem_fitmeasures(fit3_age_firstadmin)

@@

FIXME

```{r}
d_sub_prod <- filter(d_sub, !is.na(prod), !is.na(log_rt)) |>
  ungroup() |>
  mutate(log_rt_resid = resid(lm(log_rt ~ log_age))) |>
  group_by(subject_id) |>
  mutate(log_rt_0 = log_rt[1],
         log_rt_0_resid = log_rt_resid[1],
         acc_0 = long_window_accuracy[1]) |> 
  filter(!is.na(log_rt_0))

mod_nlme <- nlme(model = prod ~ SSlogis(age, Asym = 1, xmid, scale),
                 data = d_sub_prod,
                 fixed = xmid + scale ~ log_rt_0_resid,
                 random = xmid + scale ~ 1 | subject_id,
                 groups = ~ dataset_name,
                 start = c(xmid = 20, scale = 3, `xmid:log_rt_0_resid` = 1, `scale:log_rt_0_resid` = 3),
                 na.action = na.exclude, 
                 control = list(maxIter = 1000, tolerance = .1))

summary(mod_nlme)

# fixed
global_preds <- expand_grid(age = seq(min(d_sub_prod$age), 
                                      max(d_sub_prod$age), .1), 
                            log_rt_0_resid = c(quantile(d_sub_prod$log_rt_0_resid, 
                                                        c(.25,.75), 
                                                        na.rm=TRUE)))
global_preds$pred <- predict(mod_nlme, newdata = global_preds, level = 0)

#random effects
dataset_preds <- d_sub |>
  filter(!is.na(prod)) |> # filter on predictor
  group_by(dataset_name) |>
  summarise(min_age = min(age),
            max_age = max(age)) |>
  group_by(dataset_name) |>
  mutate(df = map2(min_age, max_age, ~expand_grid(age = seq(.x, .y, .1), log_rt_0_resid = c(quantile(d_sub_prod$log_rt_0_resid, 
                                                                                                     c(.25,.75), 
                                                                                                     na.rm=TRUE))))) |>
  select(-min_age, -max_age) |>
  unnest(col = "df") |>
  ungroup()

dataset_preds$pred <- predict(mod_nlme,
                              newdata = dataset_preds,
                              level = c(0,1))$predict.dataset_name

ggplot(d_sub_prod, aes(x = age, y = prod, col = as.factor(log_rt_0_resid))) + 
  geom_point(alpha = .03, pch = ".", col = "black") + 
  geom_line(aes(group = subject_id), alpha = .02, col = "black") + 
  geom_line(data = dataset_preds |>   
              filter(dataset_name %in% datasets_with_age_variation$dataset_name), 
            aes(y = pred, group = interaction(log_rt_0_resid, dataset_name)), lty="dashed", alpha=.5)+
  geom_line(data = global_preds, aes(y = pred, group = log_rt_0_resid, col = as.factor(log_rt_0_resid)), size=1)+
  scale_color_viridis(discrete=T, option = "H")+
  theme(legend.position = "none")+
  labs(y="Production", x="Age in months")

```{r}
library(brms)

d_sub_prod$age_c <- d_sub_prod$age - mean(d_sub_prod$age, na.rm = TRUE)
d_sub_prod$log_rt_0_c <- d_sub_prod$log_rt_0 - mean(d_sub_prod$log_rt_0, na.rm = TRUE)

# Define the nonlinear formula
nlform <- brms::bf(
  prod ~ 1 / (1 + exp((xmid - age_c) / exp(logscale))),
  xmid ~ 1 + log_rt_0_c  + (1 | dataset_name/subject_id),
  logscale ~ 1 + log_rt_0_c  + (1 | dataset_name/subject_id),
  # scale ~ 1 + log_rt_0_c,
  nl = TRUE
)

# xmid ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),
# scale ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),

priors <- c(
  prior(normal(0, 5), nlpar = "xmid", coef = "Intercept"),  # xmid near center of age_c
  prior(normal(1, 1), nlpar = "logscale", coef = "Intercept"), # scale > 0, mildly steep curve
  prior(normal(0, 1), nlpar = "logscale", coef = "log_rt_0_c"),
  prior(exponential(1), class = "sigma"),                # residual error
  prior(normal(0, 2), nlpar = "xmid", coef = "log_rt_0_c"),
  # prior(normal(0, 1), nlpar = "scale", lb = 0)

  # Random effects for xmid
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name:subject_id"),

  # Random effects for scale
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name:subject_id")
)
#

# Fit the model
mod_brms <- brm(
  formula = nlform,
  data = d_sub_prod,
  prior = priors,
  family = gaussian(),
  # init = 0,  # initialize all parameters to 0 on unconstrained scale (safe for centered priors)
  chains = 4, cores = 4,
  control = list(adapt_delta = 0.95),
  # backend = "cmdstanr",  # optional but faster
  save_pars = save_pars(all = TRUE),
  sample_prior = "yes"
)

new_data <- expand.grid(
  age_c = seq(min(d_sub_prod$age_c), max(d_sub_prod$age_c), length.out = 100),
  log_rt_0_c = c(-1, 0, 1)  # e.g., low, mean, high values
)

fitted_vals <- fitted(mod_brms, newdata = new_data, re_formula = NA, summary = TRUE)

new_data$fit <- fitted_vals[, "Estimate"]
new_data$lower <- fitted_vals[, "Q2.5"]
new_data$upper <- fitted_vals[, "Q97.5"]

ggplot(new_data, aes(x = age_c, y = fit, col = as.factor(log_rt_0_c))) +
  geom_line(linewidth = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = as.factor(log_rt_0_c), group = as.factor(log_rt_0_c)), 
              alpha = 0.2) +
  labs(x = "Centered Age", y = "Predicted prod (fixed effects only)") +
  theme_minimal() + 
  geom_point(data = d_sub_prod, aes(x = age_c, y = prod), col = "black") + 
  scale_color_solarized(name = "log RT at t0 (SD)") + 
  scale_fill_solarized(guide = FALSE)

```{r}
library(brms)

d_sub_prod$age_c <- d_sub_prod$age - mean(d_sub_prod$age, na.rm = TRUE)
d_sub_prod$log_rt_0_c <- d_sub_prod$log_rt_0 - mean(d_sub_prod$log_rt_0, na.rm = TRUE)

d_sub_prod$resid_log_rt_0_c <- resid(lm(log_rt_0_c ~ log(age), data = d_sub_prod))

# Define the nonlinear formula
nlform_resid <- brms::bf(
  prod ~ 1 / (1 + exp((xmid - age_c) / exp(logscale))),
  xmid ~ 1 + resid_log_rt_0_c  + (1 | dataset_name/subject_id),
  logscale ~ 1 + resid_log_rt_0_c  + (1 | dataset_name/subject_id),
  # scale ~ 1 + log_rt_0_c,
  nl = TRUE
)

# xmid ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),
# scale ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),

priors_resid <- c(
  prior(normal(0, 5), nlpar = "xmid", coef = "Intercept"),  # xmid near center of age_c
  prior(normal(1, 1), nlpar = "logscale", coef = "Intercept"), # scale > 0, mildly steep curve
  prior(normal(0, 1), nlpar = "logscale", coef = "resid_log_rt_0_c"),
  prior(exponential(1), class = "sigma"),                # residual error
  prior(normal(0, 2), nlpar = "xmid", coef = "resid_log_rt_0_c"),
  # prior(normal(0, 1), nlpar = "scale", lb = 0)

  # Random effects for xmid
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name:subject_id"),

  # Random effects for scale
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name:subject_id")
)
#

# Fit the model
resid_mod_brms <- brm(
  formula = nlform_resid,
  data = d_sub_prod,
  prior = priors_resid,
  family = gaussian(),
  # init = 0,  # initialize all parameters to 0 on unconstrained scale (safe for centered priors)
  chains = 4, cores = 4,
  control = list(adapt_delta = 0.95),
  # backend = "cmdstanr",  # optional but faster
  save_pars = save_pars(all = TRUE),
  sample_prior = "yes"
)

new_data_resid <- expand.grid(
  age_c = seq(min(d_sub_prod$age_c), max(d_sub_prod$age_c), length.out = 100),
  resid_log_rt_0_c = c(-1, 0, 1)  # e.g., low, mean, high values
)

fitted_vals <- fitted(mod_brms, newdata = new_data, re_formula = NA, summary = TRUE)

new_data_resid$fit <- fitted_vals[, "Estimate"]
new_data_resid$lower <- fitted_vals[, "Q2.5"]
new_data_resid$upper <- fitted_vals[, "Q97.5"]

ggplot(new_data_resid, aes(x = age_c, y = fit, col = as.factor(resid_log_rt_0_c))) +
  geom_line(linewidth = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = as.factor(resid_log_rt_0_c), group = as.factor(resid_log_rt_0_c)), 
              alpha = 0.2) +
  labs(x = "Centered Age", y = "Predicted prod (fixed effects only)") +
  theme_minimal() + 
  scale_color_viridis() + 
  geom_point(data = d_sub_prod, aes(x = age_c, y = prod), col = "black")

# SEM Longitudinal Missingness

FIXME

```{r}
colMeans(!is.na(d_sub_wide_fine))
```

# Additional References
